Bayesim: a tool for fast device characterization with Bayesian inference

### 2018-06-29 paper/Manuscript.tex
updated paper

\section*{Introduction}
 motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding) 
\section*{Model}
 \begin{itemize}\item background on Bayes theorem \item particulars about how it can be applied to fitting problems we're interested in \item advantages over traditional fitting approaches \item figure 1 \end{itemize}  
\begin{figure}[!ht]

\subfloat[\label{Fig:10a}]
{\includegraphics[width=0.48\columnwidth]{./figure_1a.png}}
\hfill
\subfloat[\label{Fig:10b}]
{\includegraphics[width=0.48\columnwidth]{./figure_1b.png}}
\caption{(a) Scheme (b) Probability}
\end{figure}

\section*{Software Architecture and Interface}
 \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{./figure_2.png}}
\caption{Bayesian workflow}
\end{figure}
\section*{Application Examples}
 \subsection{Ideal Diode Model} \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{./figure_3.png}}
\caption{Ideal diode}
\end{figure}\subsection{Example with Real Data} \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}  
\begin{figure}[!ht]

\subfloat[\label{Fig:40a}]
{\includegraphics[width=0.48\columnwidth]{./figure_4a.png}}
\hfill
\subfloat[\label{Fig:40b}]
{\includegraphics[width=0.48\columnwidth]{./figure_4b.png}}
\caption{Real data}
\end{figure}
\subsection{Maybe an example with a numerical model like PC1D} \subsection{Maybe a non-PV example} thermoelectrics? TIDLS? 
\section*{Conclusions}

>>>>

\section*{Introduction}
 motivation (within PV and beyond) citing examples of our application of this idea so far (Joule paper and PVSC proceeding) 
\section*{Model}
 \begin{itemize}
 \item background on Bayes theorem
 \item particulars about how it can be applied to fitting problems we're interested in
 \item advantages over traditional fitting approaches
 \item figure 1
 \end{itemize}

\begin{figure}[!ht]

\subfloat[\label{Fig:10a}]
{\includegraphics[width=0.48\columnwidth]{././figure_1a.png}}
\hfill
\subfloat[\label{Fig:10b}]
{\includegraphics[width=0.48\columnwidth]{././figure_1b.png}}
\caption{(a) Scheme (b) Probability}
\end{figure}

\section*{Software Architecture and Interface}
 \begin{itemize}\item description of structure of new code and workflow for using it (both Python scripting and command-line) \item figure 2 \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{././figure_2.png}}
\caption{Bayesian workflow}
\end{figure}
\section*{Application Examples}
 \subsection{Ideal Diode Model}
  \begin{itemize}\item validation example - ``observed'' data is just generated using the model and we show we can recover the correct input parameters \item figure 3 showing PMF (animation in ESI) \end{itemize}  \begin{figure}
{\includegraphics[width=0.7\columnwidth]{././figure_3.png}}
\caption{Ideal diode}
\end{figure}\subsection{Example with Real Data}
  \begin{itemize}\item more practical example - probably fitting resistive diode to the same SnS data we used in the Joule paper \item figure 4 showing PMF (animation in ESI) and comparison of JV curves \end{itemize}  
\begin{figure}[!ht]

\subfloat[\label{Fig:40a}]
{\includegraphics[width=0.48\columnwidth]{././figure_4a.png}}
\hfill
\subfloat[\label{Fig:40b}]
{\includegraphics[width=0.48\columnwidth]{././figure_4b.png}}
\caption{Real data}
\end{figure}
\subsection{Maybe an example with a numerical model like PC1D}
  \subsection{Maybe a non-PV example}
  thermoelectrics? TIDLS? 
\section*{Conclusions}
